Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-26 paper/paper.tex
slightly shortened legend to Figure S6

\begin{suppfig}
{\bf \Large A}\includegraphics[width=0.48\textwidth, valign=t]{figures/Validation_Figure/SNP_flow_plot.pdf}
\hspace{0.02\textwidth}
{\bf \Large B} \includegraphics[width=0.39\textwidth, valign=t]{figures/Validation_Figure/del_flow_plot.pdf}
\caption{
{\bf Flow cytometry data for \FIG{validation}.}
{\bf (A)}
Data for \FIG{validation}A.
A549 cells with the \textit{IFNL1} reporter driving LNGFR$\Delta$C-ZsGreen were infected with stocks of the indicated mutant.
After 13 hours, cells were stained for HA protein and analyzed by FACS.
Contour plots show density of all cells, and IFN+ cells are also indicated by orange dots.
Cells were classified as HA+ or IFN+ based on gates set to put 0.05\% of uninfected cells in these populations.
For infected cells, the percentage IFN+ was calculated among the HA+ cells (since these are the ones that are infected).
For uninfected cells, the percentage IFN+ was calculated among all cells, since uninfected cells do not express HA.
For each viral mutant, two independent stocks were assayed in duplicate (i.e., \#1a and \#1b are one viral stock, and \#2a and \#2b are the other).
The infections with replicate \#1 of the wild-type virus were performed at an MOI of 0.1 as determined by TCID50, and all other viruses were infected at an equivalent particle number as determined by HI assay. 
{\bf (B)}
Data for \FIG{validation}B.
The virus with the deletion in PB1 cannot be normalized by HA expression since it expresses less HA due to the lack of secondary transcription.
Therefore, all cells were infected at an equivalent MOI of 0.3 as determined by TCID50 on MDCK-SIAT1 cells for wild type and NS1stop, and on MDCK-SIAT1 cells expressing PB1~\citep{bloom2010permissive} for PB1del385to2163.
\SUPPFIG{delqPCR} shows that at these equivalent TCID50s, all variants had similar amounts of transcriptionally active virus in the absence of secondary transcription.
The percent IFN+ was calculated for \emph{all} cells (HA+ and HA-) since that is a more fair comparison for PB1del385to2163.
}
\label{suppfig:validationflow}
\end{suppfig}

>>>>

\begin{suppfig}
{\bf \Large A}\includegraphics[width=0.48\textwidth, valign=t]{figures/Validation_Figure/SNP_flow_plot.pdf}
\hspace{0.02\textwidth}
{\bf \Large B} \includegraphics[width=0.39\textwidth, valign=t]{figures/Validation_Figure/del_flow_plot.pdf}
\caption{
{\bf Flow cytometry data for \FIG{validation}.}
{\bf (A)}
Data for \FIG{validation}A.
A549 cells with the \textit{IFNL1} reporter driving LNGFR$\Delta$C-ZsGreen were infected with the indicated mutant.
After 13 hours, cells were stained for HA protein and analyzed by FACS.
Contour plots show density of all cells, and IFN+ cells are also indicated by orange dots.
Cells were classified as HA+ or IFN+ based on gates that put 0.05\% of uninfected cells in these populations.
For infected cells, the percentage IFN+ was calculated among the HA+ cells (since these are the ones that are infected).
For uninfected cells, the percentage IFN+ was calculated among all cells, since uninfected cells do not express HA.
For each viral mutant, two independent stocks were assayed in duplicate (i.e., \#1a and \#1b are one viral stock, and \#2a and \#2b are the other).
Infections with replicate \#1 of the wild-type virus were performed at an MOI of 0.1 as determined by TCID50, and all other viruses were infected at an equivalent particle number as determined by HI assay. 
{\bf (B)}
Data for \FIG{validation}B.
The virus with the deletion in PB1 cannot be normalized by HA expression since it expresses less HA due to the lack of secondary transcription.
Therefore, all cells were infected at a MOI of 0.3 as determined by TCID50 on MDCK-SIAT1 cells for wild type and NS1stop, and on MDCK-SIAT1 cells expressing PB1~\citep{bloom2010permissive} for PB1del385to2163.
\SUPPFIG{delqPCR} shows that at these equivalent TCID50s, all variants had similar amounts of transcriptionally active virus in the absence of secondary transcription.
The percent IFN+ was calculated for \emph{all} cells (HA+ and HA-) since that is a more fair comparison for PB1del385to2163.
}
\label{suppfig:validationflow}
\end{suppfig}
